A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-15 manuscript/manuscript.tex
updated reprocessing handling to match API

Provenance is stored for each pipeline run alongside the generated
derivatives and consists of parameter values used by the pipeline,
software versions used by the pipeline, a graph representation of the
underlying Nipype workflow, checksums of inputs, version of Arcana used,
version of Nipype used, subject and visit IDs used by study.

For subsequent analyses, changes with respect to any of the stored values, with
the exception of subject and visit IDs, will be flagged as a mismatch by default.
However, changes can be ignored by providing the path to the attribute to ignore
to the \emph{prov\_ignore} keyword argument at initialisation of the Processor.
Subject or visit IDs only flag a mismatch if any of the inputs, or
inputs of upstream pipelines, are of per-visit or per-subject frequency,
respectively, or per-study frequency. How provenance mismatches are handled by the
study is determined by the \emph{reprocess} flag, which is passed to the
Study on initialisation (Table \ref{tbl:reprocess-flag}).

\begin{table}
\caption{Effect of the \emph{reprocess} flag value on the
behaviour of the study when existing derivatives are found that were
derived with mismatching inputs and parameters.}
\label{tbl:reprocess-flag} 
\begin{tabular}{ll}
\hline\noalign{\smallskip}
\textbf{Reprocess value} & \textbf{Behaviour on provenance mismatch} \\
\noalign{\smallskip}\hline\noalign{\smallskip}
False (default) & Raises an exception \\
True & Mismatching derivatives will be reprocessed \\
`ignore' & Mismatches are ignored \\
`ignore\_versions' & Ignore versions, otherwise raise exception \\
`ignore\_versions\_true' & Ignore versions, otherwise the derivative will be reprocessed \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

Provenance is stored for each pipeline run alongside the generated
derivatives and consists of parameter values used by the pipeline,
software versions used by the pipeline, interface parameters,
a graph representation of the underlying Nipype workflow, checksums of inputs,
version of Arcana used, version of Nipype used, and any subject and visit IDs
that were joined over in the workflow.

For subsequent analyses, changes with respect to any of the stored provenance values will
be flagged as a mismatch, with the exception of interface package versions
(e.g. Nipype or Banana versions). How mismatches are handled depends on the \emph{reprocess} flag passed to the
Processor. If \emph{reprocess} is true then the sessions with mismatching provenance
will be reprocessed, otherwise if \emph{reprocess} is false (the default) an exception will be raised.
Changes with respect to any element in the provenance JSON document can be ignored by providing
a list of JSONPath queries to the \emph{prov\_ignore} keyword argument.
